---
title: "R Notebook"
output: html_notebook
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

#laurenedits

```{r}
data = read.csv("pokemon_alopez247.csv", header=T)
```

```{r}
summary(data)
```

```{r}
library(scatterplot3d) 
attach(pokemon) 
scatterplot3d(Defense,HP,hasGender, pch=16, highlight.3d=TRUE,
  type="h", main="3D Scatterplot")
```

```{r}
library(scatterplot3d) 
attach(pokemon) 
scatterplot3d(HP,Defense,Pr_Male, pch=16, highlight.3d=TRUE,
  type="h", main="3D Scatterplot")
```

```{r}
library(scatterplot3d)
attach(pokemon)
scatterplot3d(Defense,HP,Pr_Male, main="3D Scatterplot")
```

```{r}
library(gclus)
dta <- pokemon[c(5,6,7,8)] # data, numbers as column numbers 
dta.r <- abs(cor(dta)) # correlation
dta.col <- dmat.color(dta.r) # colors
dta.o <- order.single(dta.r) 
cpairs(dta, dta.o, panel.colors=dta.col, gap=.5,
main="Variables Ordered and Colored by Correlation" )
```

```{r}
library(neuralnet)
attach(pokemon)
scale() 
NN <- neuralnet(HP~Defense, data=pokemon, hidden = 0)
sum((predict(NN, data.frame(Defense))~HP)^2)
```

shreeves@alumni.ubc.ca

Cannot do this:
NN <- neuralnet(HP~hasGender, data=pokemon, hidden = 0)
  as it is not numeric, but is binary 

Cannot do this:
NN = neauralnet(Number ~ Name + Type_1 + Type_2 + Total + HP + Attack + Defense + Sp_Attk + Sp_Def + Speed + Generation + isLegendary + Color + hasGender + Pr_Male + Egg_Group_1 + Egg_Group_2 + hasMegaEvolution + Height_m + Weight_kg + Catch_Rate + Body_Style, data=pokemon, hidden = 0)
plot(NN) as these are non-numeric responses

```{r}
library(neuralnet)
trainNN = scaled[index,]
testNN = scaled[-index,]
set.seed(2)
NN = neauralnet(Number ~ Name + Type_1 + Type_2 + Total + HP + Attack + Defense + Sp_Attk + Sp_Def + Speed + Generation + isLegendary + Color + hasGender + Pr_Male + Egg_Group_1 + Egg_Group_2 + hasMegaEvolution + Height_m + Weight_kg + Catch_Rate + Body_Style)
plot(NN)
```


**ERROR
```{r}
pokemon <- read.csv("~/pokemon_alopez247.csv", stringsAsFactors = FALSE)
#remove NA
cleanPoke <- na.omit(pokemon)
pcPoke <- prcomp(as.matrix(cleanPoke[,c(6,8,16)]), scale. = TRUE)
summary(pcPoke)
```

