---
title: "Neural networks, Pokemon"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
data = read.csv("pokemon_alopez247.csv", header=T)
```

#Neural Networks
```{r}
library(nnet)
library(NeuralNetTools)
library(neuralnet)
set.seed(53747958)
numeric_col <- c(5:12, 16, 20:21)
pokemon[,numeric_col] <- scale(pokemon[,numeric_col])
train<-sample(1:nrow(pokemon),505)
testset<-poke[-train,]
trainset<-poke[train,]
```

```{r}
library(gclus)
library(nnet)
library(NeuralNetTools)
set.seed(1995)
spoke <- cbind(scale(trainset[,6:11]), factor(trainset$isLegendary))
colnames(spoke)[7] <- "isLegendary"
spoke<-data.frame(spoke)
nnpoke <- nnet(factor(isLegendary)~., data=spoke, size=9)
table(trainset$isLegendary, predict(nnpoke, type="class"))
plotnet(nnpoke)
```

```{r}
spoke
```

```{r}
spoketest <- cbind(scale(testset[,6:11]), factor(testset$isLegendary))
colnames(spoketest)[7] <- "isLegendary"
spoketest<-data.frame(spoketest)
table(spoketest$isLegendary, predict(nnpoke, newdata=spoketest, type="class"))
```

```{r}
attach(data)
trainsetg<-trainset[which(hasGender=='True'),]
testsetg<-testset[which(hasGender=='True'),]
trainsetg<-na.omit(trainsetg)
trainsetg
testsetg<-na.omit(testsetg)
testsetg
```

##Neural Net predicting Pr_Male
```{r}
set.seed(906534)
library(nnet)
library(NeuralNetTools)
library(neuralnet)
nnmale <- neuralnet(Pr_Male ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed,data=trainsetg, hidden=3, threshold=0.01)
#nnmale <- neuralnet(Pr_Male ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed + Weight_kg + Height_m,data=trainsetg, hidden=5, threshold=0.01)
plotnet(nnmale)
mse<-mean((compute(nnmale, testsetg[,6:11])$net.result-testsetg$Pr_Male)^2)
#mse<-mean((compute(nnmale, testsetg[,c(6:11, 20:21)])$net.result-testsetg$Pr_Male)^2)
mse
```

Optimizing number of nodes in first layer
```{r}
for(i in 1:5){
  nnmaletr <- neuralnet(Pr_Male ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed,data=trainsetg, hidden=c(i,3), threshold=0.01)
  print(paste("Number of hidden layer variables in first layer:", i))
  print(paste("MSE: ", mean((compute(nnmaletr, testsetg[,6:11])$net.result-testsetg$Pr_Male)^2)))
}
```

Optimizing number of nodes in second layer
```{r}
for(i in 1:5){
  nnmaletr <- neuralnet(Pr_Male ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed,data=trainsetg, hidden=c(4,i), threshold=0.01)
  print(paste("Number of hidden layer variables in second layer:", i))
  print(paste("MSE: ", mean((compute(nnmaletr, testsetg[,6:11])$net.result-testsetg$Pr_Male)^2)))
}
```
MSE with 2 hidden layers and 4 and 3 nodes: 0.04011755
MSE with 1 hidden layer and 3 nodes: 0.03988659

```{r}
linmod<-lm(Pr_Male ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed + Weight_kg + Height_m,data=trainsetg)
mean((predict(linmod,newdata=testsetg)-testsetg$Pr_Male)^2)
```
This is pretty close to our neural net modeled above when we use 1 hidden layer and 3 nodes. 

##Neural net predicting hasGender
```{r}
library(gclus)
library(nnet)
library(NeuralNetTools)
set.seed(1995)
gpoke <- cbind(scale(trainset[,c(6:11, 20:22)]), factor(trainset$hasGender))
colnames(gpoke)[10] <- "hasGender"
gpoke<-data.frame(gpoke)
nngend <- nnet(factor(hasGender)~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed + Catch_Rate + Height_m + Weight_kg, data=gpoke, size=5)
plotnet(nngend)
table(trainset$hasGender, predict(nngend, type="class"))
```
It appears that our neural net is effective in predicting hasGender, and also easy to generate an overfitted model for. 
1 hidden layer with 11 nodes appears to overfit the model, 
         1   2
  False 45   0
  True    0 460
  
Instead 1 hidden layer with 5 nodes appears to have a reasonable misclassification without totally overfitting. Let's try this on gspoketest,

```{r}
gpoketest <- cbind(scale(trainset[,c(6:11, 20:22)]), factor(testset$hasGender))
colnames(gpoketest)[10] <- "hasGender"
gpoketest<-data.frame(gpoketest)
table(gpoketest$hasGender, predict(nngend, newdata=gpoketest, type="class"))
```

##Neural net predicting Generation
```{r}
library(gclus)
library(nnet)
library(neuralnet)
library(NeuralNetTools)
set.seed(19127395)
#nnGeneration <- neuralnet(Generation ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed + Pr_Male,data=trainsetg, hidden=5, threshold=0.01)
nnGeneration <- neuralnet(Generation ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed,data=trainsetg, hidden=5, threshold=0.01)
plotnet(nnGeneration)
mse<-mean((compute(nnGeneration, testsetg[,6:11])$net.result-testsetg$Generation)^2)
mse
```

Optimizing number of nodes in first layer
```{r}
for(i in 1:5){
  nnmaletr <- neuralnet(Generation ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed,data=trainsetg, hidden=3, threshold=0.01)
  print(paste("Number of hidden layer variables in first layer:", i))
  print(paste("MSE: ", mean((compute(nnmaletr, testsetg[,6:11])$net.result-testsetg$Pr_Male)^2)))
}
```

```{r}
linmod<-lm(Generation ~ Attack + Defense + HP + Sp_Atk + Sp_Def + Speed,data=trainsetg)
mean((predict(linmod,newdata=testsetg)-testsetg$Generation)^2)
```