---
title: "R Notebook"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pokemon<-read.csv("pokemon_alopez247.csv")
poke<-data.frame(pokemon)
```

```{r}
pcapoke <- prcomp(as.matrix(poke[,c(6:11, 20:21)]), scale.=TRUE)
summary(pcapoke)
biplot(pcapoke)
```


```{r}
round(pcapoke$rotation[,1:2], 2)
```


```{r}
poke[order(pcapoke$x[,1], decreasing=TRUE)[1:4] , c(1:11, 20:21)]
```

```{r}
poke[order(pcapoke$x[,2], decreasing=TRUE)[1:4] , c(1:11, 20:21)]
```

```{r}
poke[order(pcapoke$x[,1], decreasing=TRUE)[1:20],]
```

Majority are of the legendary type


```{r}
lda.pred<-predict(leggenlda1,poke1)
lda.class<-lda.pred$class
table(lda.class,poke1$isLegendary)
```

Yea, this is still a naive classifier, NOT VERY USEFUL!

Let's try a linear model, see if PC1 and PC2 are any good at predicting Pr_Male:

```{r}
linmod<-lm(poke1$Pr_Male~pcgenleg[,1]+pcgenleg[,2])
summary(linmod)
linmod<-lm(poke1$Pr_Male~pcgenleg[,1])
summary(linmod)
plot(pcgenleg[,1],poke1$Pr_Male)
abline(linmod)
```

Ok, so the second model is statistically significant. So let's try to interpret this now. The intercept on this linear model is 0.55, which is already above 50%. Oh man that graph looks like garbage. I don't think PCA really did anything here...


```{r}
# linmod<-lm(poke1$Catch_Rate~pcgenleg[,1]+pcgenleg[,2])
# summary(linmod)
linmod<-lm(poke1$Catch_Rate~pcgenleg[,1])
summary(linmod)
plot(pcgenleg[,1],poke1$Catch_Rate)
abline(linmod)
```

Ok, now we're talking. So it looks like PC1 is correlated with the harder to catch Pokemon rather than the legendary ones. Probably a good time to start a new file, this is getting messy...

```{r}
set.seed(1995)
train<-sample(1:nrow(poke),432)
poke.test<-poke[-train,]
poke.train<-poke[train,]
```