---
title: "Lasso"
author: "Kathryn Lecha"
date: '2019-03-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pokemon<-read.csv("data/pokemon_alopez247.csv")
```

## LASSO

Let's try using LASSO to remove predictors from the linear model


```{r}
library(glmnet)
set.seed(53342)

lasso <- function(x, y, grid){
  lassomod<-cv.glmnet(x,y, family="binomial", alpha=1, lambda=grid)
  plot(lassomod)
  plot(lassomod$glmnet.fit, label=TRUE, xvar="lambda")
  lammin <- lassomod$lambda.min
  lam1se <- lassomod$lambda.1se
  lasimmin <- glmnet(x,y,alpha = 1, lambda=lammin)
  lasim1se <- glmnet(x,y,alpha = 1, lambda=lam1se)
}
```

### Predicting isLegendary

```{r}
pkmn<-data.frame(pokemon, stringsAsFactors = TRUE)
pkmn[is.na(pkmn)] <- 0
x <- data.matrix(pkmn)[,-13]
y <- as.integer(as.logical(pkmn$isLegendary))
grid<-exp(seq(-1.5,-8.25,length=100))
lasso(x, y, grid)
```

```{r}
coef(lasimmin)
coef(lasim1se)
```


Overall, the most important predictor is hasGender. This is not surprising and matches the rest of the analysis.
However, it is interesting and worth point out that after Pr_Male is removed, it becomes a more more promenent predictor. This is because Pr_Male is in many ways repeat data from hasGender. Any pokemon without a gernder has no probablity of being male. 

### Predicting hasGender

```{r}
pkmn<-data.frame(pokemon, stringsAsFactors = TRUE)
x <- data.matrix(pkmn)[,-c(15, 16)]
y <- as.integer(as.logical(pkmn$hasGender))
grid<-exp(seq(-2,-9,length=200))
lasso(x, y, grid)
```

Removed $pokemon\$Pr\_Male$ bc is dependent on $pokemon\$hasGender$ and minimum was $\lim(LogLambda->-infinity)$.

```{r}
coef(lasimmin)
```

```{r}
coef(lasim1se)
```

Looks like $pokemon\$isLegendary$ is the most important variable...

```{r}
poke0<-data.frame(pokemon)
poke1<-poke0[which(poke0$hasGender=='True'),]
attach(poke0)
head(poke1)
x <- data.matrix(poke1)[,-16]
y <- poke1$Pr_Male
grid<-exp(seq(-1,-9,length=150))
lassomod<-cv.glmnet(x,y, alpha=1, lambda = grid)
plot(lassomod)
plot(lassomod$glmnet.fit, label=TRUE, xvar="lambda")
lammin <- lassomod$lambda.min
lam1se <- lassomod$lambda.1se
lasimmin <- glmnet(x,y,alpha = 1, lambda=lammin)
lasim1se <- glmnet(x,y,alpha = 1, lambda=lam1se)
```

```{r}
coef(lasimmin)
```

```{r}
coef(lasim1se)
```

One thing to note is that this appears to have a large standard deviation.... The true minimum is at 19 variables but one standard deviation from that gives ~8 variables.


```{r}
linmod <- lm(poke$Pr_Male ~ Type_2 + HP +Attack +hasGender + Egg_Group_1 + Egg_Group_2 + Catch_Rate + Body_Style + hasGender*HP, data= poke)
summary(linmod)

mean((linmod$residuals)^2)
```



##Fitting interactions
Reference:
https://strakaps.github.io/post/glinternet/

```{r}
#install.packages("glinternet")
library("glinternet")
library(dplyr)
```


ˆ
```{r}
getX <- function(poke){
  # impute the median for the continuous variables
  i_num <- sapply(poke, is.numeric)
  poke[, i_num] <- apply(poke[, i_num], 2, function(x) ifelse(is.na(x), median(x, na.rm=T), x))
  
  # impute empty categories
  poke[, !i_num] <- apply(poke[, !i_num], 2, function(x) {
    x[x==""] <- "empty"
    x[is.na(x)] <- "missing"
    x
  })
  
  # get the numLevels vector containing the number of categories
  X <- poke
  X[, !i_num] <- apply(X[, !i_num], 2, factor) %>% as.data.frame()
  numLevels <- X %>% sapply(nlevels)
  numLevels[numLevels==0] <- 1
  
  
  # make the categorical variables take integer values starting from 0
  X[, !i_num] <- apply(X[, !i_num], 2, function(col) as.integer(as.factor(col)) - 1)
}
```

```{r}
getmainEffects <- function(coefs){
  print(coefs$mainEffects)

  idx_num <- (1:length(i_num))[i_num]
  idx_cat <- (1:length(i_num))[!i_num]
  print(names(numLevels)[idx_cat[coefs$mainEffects$cat]])
  print(names(numLevels)[idx_num[coefs$mainEffects$cont]])
  
  print(coefs$mainEffectsCoef)
}
```



### isLegendary
```{r}
poke <- data.frame(pokemon)

y <- as.integer(as.logical(poke$isLegendary))

#1,2 are unique and not useful
poke <- poke[, -c(1,2, 13)]
head(poke)

getX(poke)
```


```{r}
cv_fit <- glinternet.cv(X, y, numLevels)
plot(cv_fit)
```

```{r}
i_1Std <- which(cv_fit$lambdaHat1Std == cv_fit$lambda)
coefs <- coef(cv_fit$glinternetFit)[[i_1Std]]
coefs
```

####Main Effects (without interactions)

```{r}
getmainEffects(coefs)
```

Main Effects are Total, Sp_Atk, Sp_Def, and Weight

####Interactions
```{r}
coefs$interactions
```

The $catcat$ tells us that there is no interaction between the categorical variables

Three pairs of continuous variables have interactions:  
$(1,5)$, $(1,6)$, and $(1,11)$
Total interacts with Sp_Atk, Sp_Def, and (i counted catch rate but i think ti should be weight?), which is interesting.

```{r}
coefs$interactionsCoef$contcont
```

There is one interaction between categorical and continuous variables:
Sp_Atk and Type_1
```{r}
coefs$interactionsCoef$catcont

```

####MSE
```{r}
sqrt(cv_fit$cvErr[[i_1Std]])

```
MSE of 0.09163895


##LASSO with interactions with hasGender Removed on Total

```{r}
#install.packages("glinternet")
library("glinternet")
library(dplyr)

```

```{r}
poke <- data.frame(pokemon)

poke<-poke[which(poke$hasGender=='True'),]
y <- as.integer(poke$Total)

#1,2 are unique and not useful
#removed hasGender
#using total as response
poke <- poke[, -c(1,2, 5, 15)]
head(poke)

getX(poke)
```


```{r}
cv_fit <- glinternet.cv(X, y, numLevels)
#plot(cv_fit)
```

```{r}
i_1Std <- which(cv_fit$lambdaHat1Std == cv_fit$lambda)
coefs <- coef(cv_fit$glinternetFit)[[i_1Std]]
coefs
```

####Main Effects (part without interactions)

```{r}
getmainEffects(coefs)
```

Main Effects are "HP", "Attack", "Defense", "Sp_Atk", "Sp_Def", "Speed", and "Catch_Rate"

####Interactions
```{r}
coefs$interactions
```

There are no significant interactions

####MSE
```{r}
sqrt(cv_fit$cvErr[[i_1Std]])

```
MSE of 0.812088


##LASSO with interactions with hasGender Removed on isLegendary

```{r}
poke <- data.frame(pokemon)
y <- as.integer(poke$isLegendary)


#1,2 are unique and not useful
#removed hasGender
#using islegendary as response
poke <- poke[, -c(1,2, 13, 15)]
head(poke)

getX(poke)
```


```{r}
cv_fit <- glinternet.cv(X, y, numLevels)
plot(cv_fit)
```

```{r}
i_1Std <- which(cv_fit$lambdaHat1Std == cv_fit$lambda)
coefs <- coef(cv_fit$glinternetFit)[[i_1Std]]
coefs
```

####Main Effects (part without interactions)

```{r}
getmainEffects(coefs)
```

Main Effects are "HP", "Attack", "Defense", "Sp_Atk", "Sp_Def", "Speed", and"Catch_Rate"

####Interactions
```{r}
coefs$interactions
```
Continuous interactions : Hp and Type_1
mix: Sp_Atk and Egg_Group_1

####MSE
```{r}
sqrt(cv_fit$cvErr[[i_1Std]])

```

MSE of 0.05