---
title: "KNN"
author: "Kat"
date: '2019-03-26'
output: html_document
---

# A study in the effects of Gender

It looks like weight, speed, hieght. Generation 6 has a 100% female rate but no 100% male-> is the only gen here that does that
isLegendary has more 100% male than 100% female- one 0.5%

* i think colour is really interesting-> blue, ___?, and red are all higher percentage male while pink has higher percentage female (pink is a more stereotypically feminine color?)
* fairy egg group 1 and 2 also has a higher percentage female
* has mega evolution is higher percentage of being male
* looks like higer percentage male means slightly taller height? (still mostly centered around 1m)
* looks like higer percentage male means heavier?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(fastDummies)
library(ggplot2)
library(FNN)
```

```{r}
pokemon<-read.csv("data/pokemon_alopez247.csv")
```


##KNN

### Data Processing

```{r}
poke<-data.frame(pokemon)
#remove unique identifiers
poke<-poke[,-c(1,2)]
```

This block removes all NA values for Pr_Male-> this is helpful for most analysis on Pr_Male.
```{r}
# the new dataset poke has all na values fr Pr_Male removed
# almost all legendary pokemon are removed
poke<-poke[which(poke$hasGender=='True'),]
head(poke)
```

Converting string categorical labels to numeric
```{r}
poke$isLegendary <- (as.numeric(poke$isLegendary) - 1)
poke$hasMegaEvolution <- (as.numeric(poke$hasMegaEvolution) - 1)
poke$hasGender <- (as.numeric(poke$hasGender) - 1)
```

Convert Numerical columns to Dummy Columns
```{r}
results <- fastDummies::dummy_cols(poke,  remove_first_dummy = TRUE)
# Removing repeats (without dummies)
poke<-results[, -c(1,2,12, 15, 16, 17,21)]
head(poke)
```

###KNN Regression on Pr_Male

```{r}
# remove HP, Catch_Rate
poke3<-data.frame(poke[,-c(2, 14)])
poke3
```

```{r}
# removing gendered statistics (might add noise)
X = poke3[,-c(8,9,10)]
y = poke3$Pr_Male
```


#### K=20

```{r}
plot(poke$Pr_Male, type ="p")
knnr20 <- knn.reg(X, y=y, k = 20)
lines(knnr20$pred, col="green", lwd=1)
```

Looks like it primarily sits around 50% regardless... Verifying by CV results. knnreg by default returns cross validated results
```{r}
knnr20$R2Pred
knnr20$PRESS
```

```{r}
mean((y - knnr20$pred[i])^2)
```
MSE = 0.0614

```{r}
plot_diff = function(knn, X, y, colour){
  name<-colnames(X)
  
  for(j in 1:length(name)){
    plot(y~X[,j], xlab = name[j])
    lines(knnr20$pred, col=colour, lwd=1)
  }
  
}

plot_diff(knnr20, X, y, "green")

```
Looks like Total, HP, Sp_Atk, Sp_Def, Speed, Generation, Height_m, and Weight_kg have some sort of relationship with Pr_Male. Height, Weight, and Speed might be explained by the animal kingdom views? It's a video game though....

#### k = 30


```{r}
plot(poke$Pr_Male, type ="p")
knnr30 <- knn.reg(poke[,-c(2, 14, 16)], y=poke$Pr_Male, k = 30)
lines(knnr30$pred, col="blueviolet", lwd=1)
```

```{r}
knnr30$R2Pred
knnr30$PRESS
```

```{r}
mean((y - knnr20$pred[i])^2)
```


```{r}
plot_diff(knnr30, X, y, "blueviolet")
```


#### k=10

```{r}
plot(y, type ="p")
knnr10 <- knn.reg(X, y=y, k = 10)
lines(knnr10$pred, col="aquamarine4", lwd=1)
```

```{r}
knnr10$R2Pred
knnr10$PRESS
```

```{r}
mean((y - knnr10$pred[i])^2)
```


```{r}
plot_diff(knnr10, X, y, "aquamarine4")
```