---
title: "KNN"
author: "Kat"
date: '2019-03-26'
output: html_document
---


#looks like weight, speed, hieght
# Generation 6 has a 100% female rate but no 100% male-> is the only gen here that does that
# isLegendary has moew 100% male than 100% female- one 0.5%

#i think colour is really interesting-> blue, ___?, and red are all higher percentage male while pink has higher percentage female (pink is a more stereotypically feminine color?)
# fairy egg group 1 and 2 also has a higher percentage female
#has mega evolution is higher percentage of being male
#looks like higer percentage male means slightly taller height? (still mostly centered around 1m)
##looks like higer percentage male means heavier?

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##KNN

```{r}
pokemon<-read.csv("pokemon_alopez247.csv")
poke<-data.frame(pokemon)
#remove unique identifiers
poke<-poke[,-c(1,2)]
```

This block removes all NA values for Pr_Male-> this is helpful for most analysis on Pr_Male.
```{r}
#the new dataset poke2 has all na values fr Pr_Male removed
poke2<-poke[which(poke$hasGender=='True'),]
poke2
```


```{r}
poke2$isLegendary <- (as.numeric(poke2$isLegendary) - 1)
poke2$hasMegaEvolution <- (as.numeric(poke2$hasMegaEvolution) - 1)
poke2$hasGender <- (as.numeric(poke2$hasGender) - 1)
```

```{r}
library(fastDummies)
results <- fastDummies::dummy_cols(poke2,  remove_first_dummy = TRUE)
results
```
Removing repeats (without dummies)
```{r}
poke3<-results[, -c(1,2,12, 15, 16, 17,21)]
head(poke3)
poke2<-poke3
```


###KNN Regression on Pr_Male
on to the regression!

```{r}
library(ggplot2)
library(FNN)
poke3<-data.frame(poke2[,-c(2, 14, 16)])
plot(poke2$Pr_Male, type ="p")
knnr20 <- knn.reg(poke2[,-c(2, 14, 16)], y=poke2$Pr_Male, k = 20)
lines(knnr20$pred, col="green", lwd=1)
```
knnreg by default returns cross validated results
```{r}
knnr20$R2Pred
knnr20$PRESS
```

```{r}
mse<-NA
for(i in 1:nrow(poke2)){
  mse[i]<- (poke2$Pr_Male[i] - knnr20$pred[i])^2
}
mean(mse)
```


```{r}
poke4<-poke[which(poke$hasGender=='True'),]
poke4<-data.frame(poke4[-c(2,14,16)])

name<-list("Type_1", "Total", "HP", "Attack", "Defense", "Sp_Atk", "Sp_Def", "Speed", "Generation", "isLegendary", "Colour", "hasGender", "Egg_Group_1", "hasMegaEvolution", "Height_m", "Weight_kg", "Catch_Rate", "Body_Style")


for(j in 1:ncol(poke3)){
  plot(poke2$Pr_Male~poke4[,j], xlab = name[j])
  lines(knnr20$pred, col="green", lwd=1)
}

```


Using k = 30


```{r}
library(ggplot2)
library(FNN)
poke3<-data.frame(poke2[,-c(2, 14, 16)])
plot(poke2$Pr_Male, type ="p")
knnr30 <- knn.reg(poke2[,-c(2, 14, 16)], y=poke2$Pr_Male, k = 30)
lines(knnr30$pred, col="blueviolet", lwd=1)
```

```{r}
knnr30$R2Pred
knnr30$PRESS
```

```{r}
mse<-NA
for(i in 1:nrow(poke2)){
  mse[i]<- (poke2$Pr_Male[i] - knnr30$pred[i])^2
}
mean(mse)
```


```{r}

for(j in 1:ncol(poke3)){
  plot(poke2$Pr_Male~poke4[,j], xlab = name[j])
  lines(knnr30$pred, col="green", lwd=1)
}

```


Then using k = 10

```{r}
library(ggplot2)
library(FNN)
poke3<-data.frame(poke2[,-c(2, 14, 16)])
plot(poke2$Pr_Male, type ="p")
knnr10 <- knn.reg(poke2[,-c(2, 14, 16)], y=poke2$Pr_Male, k = 10)
lines(knnr10$pred, col="aquamarine4", lwd=1)
```

```{r}
knnr10$R2Pred
knnr10$PRESS
```

```{r}
mse<-NA
for(i in 1:nrow(poke2)){
  mse[i]<- (poke2$Pr_Male[i] - knnr10$pred[i])^2
}
mean(mse)
```


```{r}

for(j in 1:ncol(poke3)){
  plot(poke2$Pr_Male~poke4[,j], xlab = name[j])
  lines(knnr10$pred, col="darkcyan", lwd=1)
}

```
